Testing Characteristics of the Linux Page Replacement Policy

### 2014-04-10 paper.tex
add graph

>>>>

%--------------------------------------------%
\begin{figure}[h]
\begin{tikzpicture}
\begin{axis}[
    title = {Random vs. Sequential Access},
    width=8cm,
    xtick={1, 2},
    xticklabels={1, 2},
    grid=major,
    ybar, 
    bar width=10pt, 
    ylabel=Page Faults, 
    xlabel=Case, 
    ymin=0, 
    enlarge x limits={abs=1}
    ]

\addplot[
    fill=red!25,
    error bars/.cd,
        y dir=both,
        y explicit
] 
table [y error=error] {
x   y           error    label
1   9862.00   220.40 1
2   4789.00   713.83 2
};
\end{axis}
\end{tikzpicture}
\end{figure}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|r|r|}
\hline
{\bf Phase } & {\bf Case} & {\bf Page Faults} & {\bf Error } \\
\hline
1 & 1 & 9862.00 & $\pm$ 220.40 \\
& 2 & 4789.00 & $\pm$ 713.83 \\

\hline
\end{tabular}
\caption{ \label{rawio} Working Set versus LRU test data
{\em  Description  }}
\end{center}
\end{table}
